Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
Therapist portal

\subsection{Central Server}
The {\em Central Server}, see Figure \ref{fig:tech}, faciliates communication between all the {\em Kimbee Game} instances and the {\em Therapist Portal}. It is written in Node JS and stores data in a MongoDB instance. We also do audio encoding to create playable audio files from child microphone data obtained from {\em Kimbee Game} instances.

\subsubsection{Data Models}
  The server has three data models: recordings, children, and therapists. Recordings are the encoded microphone encodings and recognition data from the {\em Kimbee Game} instances. They are tied to a particular game instance via a unique token generated by the {\em Kimbee Game}. Children are models created by therapists to effectively ``hook into'' recordings. They specify a name for the child, and their token obtained from their {\em Kimbee Game} instance. Future recordings are then relayed to the therapist from this particular {\em Kimbee Game} instance. Finally, therapists are the authenticated user records that contain a user email and password and provides access into the therapist portal.

\subsubsection{Audio Encoding \& Recording Storage}
  When a audio file is recieved by a {\em Kimbee Game} instance, we encode it into a WAV file by interleaving the left and right buffer channels from the microphone. This file is then compressed and stored into the database as a recording. The recognition data, whether the {\em Kimbee Game} instance thinks the recording was correct, and the target word are also stored with the recording model.

@@

>>>>

\subsection{Central Server}
The {\em Central Server}, see Figure \ref{fig:tech}, faciliates communication between all the {\em Game} instances and the {\em Therapist Portal}. It is written in Node JS and stores data in a MongoDB instance. We also do audio encoding to create playable audio files from child microphone data obtained from {\em Kimbee Game} instances.

\subsubsection{Data Models}
  The server has three data models: recordings, children, and therapists. Recordings are the microphone encodings and recognition data from the {\em Game} instances. They are tied to a particular game instance via a unique token generated by the {\em Game}. Children are models created by therapists to effectively ``hook into'' recordings. They specify a name for the child, and their token obtained from their {\em Game} instance. Future recordings are then relayed to the therapist from this particular {\em Game} instance. Finally, therapists are the authenticated user records that contain a user email and password and provides access into the therapist portal.

\subsubsection{Audio Encoding \& Recording Storage}
  When a audio file is recieved by a {\em Game} instance, we encode it into a WAV file by interleaving the left and right buffer channels from the microphone. This file is then compressed and stored into the database as a recording. The recognition data (whether the {\em Game} instance thinks the recording was correct) and the target word are also stored with the recording model.

@@

The {\em Therapist Portal}, see Figure \ref{fig:tech}, is the application the therapist will use to track his or her student's progress and listen to the student's audio recordings. It is written in Javascript using the jQuery library with Bootstrap for the design elements and look of the page.
